To be FAIR: Theory Specification Needs an Update

### 2025-06-20 action_letter.Rmd
Update action_letter.Rmd

[x] Headings should not be numbered.
[x] Tables and Figures should be uploaded separately and not positioned in the text (although it is fine to indicate where they should be inserted).
[] Figures should be uploaded in their native format (the program they were created in) at 300 dpi. Acceptable figure file formats include MS Office files (DOC, PPT, XLS), Adobe Illustrator (AI), JPG, EPS, and PDF.
[x] References should be done with hanging indents using APA style. 
[] If you want to add the doi that is good.  But do not put in the search criteria for retrieving a document that has been published in a book or journal. WHAT??
```

We have 
Upload tables separately: tab_meehl.csv
Upload figures separately: ec_visio.pdf, git_branches.png, git_compare_short.png

@@

We understand that striking the balance between the conceptual and technical details is the very challenge of this paper. In the revision we have tried to explain technical details in even simpler language.
The most important change we have made, as requested by Reviewer #2, is to move the tutorial parts of the paper into package vignettes.
We still leave a conceptual overview of the tutorial in simpler language because we do want readers of the paper to come away with some idea of what making a theory FAIR entails, and because these general principles are not tied to the R-pacakge and our specific implementation (they could be implemented using other infrastructures).

@@

We appreciate the Editor’s meta-scientific comparison of the emergence of conventions in human genetics to the (current wave of) more top-down nature of open science reforms in psychology, which by-and-large also originated in grass-roots initiatives.

@@

To address this comment, in the Revision, we repeatedly refer to the *potential* impact of FAIR theory, thus making it clear that we do not assume that this impact will be automatic nor guaranteed. Furthermore, we acknowledge in the Limitations section that empirical evidence for these potential benefits remains to be evaluated:

@@

We thank the Reviewer for their thoughtful and encouraging review.
We appreciate the Reviewer's recognition of the relevance and potential impact of FAIR theory—not only within psychology, but also in related disciplines.
We have sought to address all comments, and feel that doing so has improved the quality of the manuscript.

@@

As suggested, we now briefly mention the R-package in the abstract:

@@

We have done as requested, and additionally, include a sentence in the first paragraph to pre-emptively address readers' concerns that FAIR theory may only be relevant for those who have adopted a specific paradigm:

>>>>

[x] Headings should not be numbered.
[x] Tables and Figures should be uploaded separately and not positioned in the text (although it is fine to indicate where they should be inserted).
[] Figures should be uploaded in their native format (the program they were created in) at 300 dpi. Acceptable figure file formats include MS Office files (DOC, PPT, XLS), Adobe Illustrator (AI), JPG, EPS, and PDF.
[x] References should be done with hanging indents using APA style. 
[] If you want to add the doi that is good.  But do not put in the search criteria for retrieving a document that has been published in a book or journal. 
```

In response to your request, we have: 
- uploaded tables separately: tab_meehl.csv
- uploaded figures separately: ec_visio.pdf, git_branches.png, git_compare_short.png

@@

We understand that striking the balance between the conceptual and technical details is the very challenge of this paper. In the revision we have tried to explain technical details in even simpler language.
The most important change we have made, as requested by Reviewer #2, is to move the tutorial parts of the paper into package vignettes.
We still leave a conceptual overview of the tutorial in simpler language because we do want readers of the paper to come away with some idea of what making a theory FAIR entails. Note that these general principles are neither tied to the specific R-pacakge not to our specific implementation. Importantly, they could be implemented using an entirely different infrastructure.

@@

We appreciate the Editor’s meta-scientific comparison of the emergence of conventions in human genetics to the (current wave of) more top-down nature of Open Science reforms in Psychology, which by-and-large also originated in grass-roots initiatives.

@@

To address this comment, in the revision, we repeatedly refer to the *potential* impact of FAIR theory, thus making it clear that we do not assume that this impact will be automatic or guaranteed. Furthermore, we acknowledge in the Limitations section that empirical evidence for these potential benefits remains to be evaluated:

@@

We thank the Reviewer for their thoughtful and encouraging review.
We appreciate the Reviewer's recognition of the relevance and potential impact of FAIR theory --- not only within psychology, but also in related disciplines.
We have sought to address all comments, and feel that doing so has improved the quality of the manuscript.

@@

As suggested, we now briefly mention the R package in the abstract:

@@

We have done as requested, and additionally, include a sentence in the first paragraph to pre-emptively address readers' concerns that FAIR theory may only be relevant for those who have adopted a specific philosophical paradigm:
